Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-01-26 inst/examples/20170125-Manuscript-FK.Rmd
Fennica analyses mod

# Selected catalogue with selected years
df <- filter(df, catalog == catalogue & publication_place %in% places & !is.na(period)) %>%
             group_by(period, publication_place) %>%
             summarise(n = n(), paper = sum(paper, na.rm = TRUE)) %>%
	     mutate(paper_per_title = paper/n)

theme_set(theme_bw(20))
p <- ggplot(df, aes(x = period, y = paper_per_title)) +
     geom_bar(stat = "identity", position = "dodge", aes(fill = publication_place), color = "black") +
     ylab("Paper per title (sheets)") +
     xlab("Publication period") +
     #scale_color_manual(values = c("blue", "darkgreen")) + 
     # 	 scale_size_discrete(range = c(2, 8)) +
     guides(fill = guide_legend(reverse = TRUE, title = "Place"), color = "none") 
print(p)
```

@@

```{r bookprod, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
minyear <- 1640
maxyear <- 1828

df.turku <- df0 %>% filter(publication_year >= minyear & publication_year <= maxyear) %>%
              filter(publication_place == "Turku") %>%
	      group_by(catalog, publication_year) %>%
	      summarize(n.turku = n())

df.all <- df0 %>% filter(publication_year >= minyear & publication_year <= maxyear) %>%
	      group_by(catalog, publication_year) %>%
	      summarize(n.all = n())

df <- full_join(df.all, df.turku) %>%
        filter(!is.na(n.turku)) %>%
        mutate(f.turku = n.turku/n.all)

p <- ggplot(df, aes(x = publication_year, y = f.turku)) +
       geom_line(aes(color = catalog), size = 1) +
       scale_y_continuous(labels = scales::percent) +
       scale_color_manual(values = c("darkblue", "red")) +
       ylab("Percentage (%)") +
       xlab("Publication year") +
       guides(color = guide_legend(title = "Catalogue")) +
       ggtitle("Documents published in Turku")

print(p)
```

>>>>

# Selected catalogue with selected years
df <- filter(df, catalog == catalogue & publication_place %in% places & !is.na(period) & !is.na(paper))

df <- df %>% group_by(period, publication_place) %>%
             summarise(n = n(), paper = sum(paper, na.rm = TRUE)) %>%
	     mutate(paper_per_title = paper/n)

theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_place, y = paper_per_title)) +
     geom_bar(stat = "identity", position = "dodge", aes(fill = period), color = "black") +
     ylab("Paper per title (sheets)") +
     xlab("Publication period") +
     #scale_color_manual(values = c("blue", "darkgreen")) + 
     # 	 scale_size_discrete(range = c(2, 8)) +
     guides(fill = guide_legend(reverse = TRUE, title = "Place"), color = "none") 
print(p)

kable(df)
```

@@

```{r bookprod, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
minyear <- 1640
maxyear <- 1828 
df <- df0 %>% filter(!is.na(publication_place)) 
df$myplace <- df$publication_place
df$myplace[!df$myplace == "Turku"] <- "Other"

df <- df %>%  filter(publication_decade >= minyear & publication_decade <= maxyear) %>%
	      group_by(catalog, publication_decade, myplace) %>%
	      summarize(n = n())

pics <- list()
for (cat in unique(df$catalog)) {
  dfs <- subset(df, catalog == cat)
  p <- ggplot(dfs, aes(x = publication_decade, y = n)) +
       geom_bar(aes(fill = myplace), color = "black", stat = "identity", position = "stack") +
       scale_fill_manual(values = c("gray", "black")) +
       ylab("Title count") +
       xlab("Publication decade") +
       guides(fill = guide_legend(title = "Place")) +
       ggtitle(cat) +
       xlim(values = c(min(df$publication_decade), max(df$publication_decade)))
  pics[[cat]] <- p
}

library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], nrow = 2)
```
